Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-24 paper/paper.tex

\begin{figure}
\begin{tabular}{ l l l }
  $s:$ & Title & Lorem ipsum dolor sit amet, consectetur adipiscing elit \\
  & Author & Doe, John \\
  & Affiliation & University of Foo \\
  & Co-authors & Smith, John; Chen, Wang\\
  & Year & 2015\\
\end{tabular}

\caption{An example of signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\label{fig:signature}
\end{figure}

@@

\glnote{Figure required here (Eamonn)}

@@

\glnote{Add a figure showing the three possible splits}

@@

As part of this study, we also publicly release the annotated data extracted
from the INSPIRE platform, and on which our experiments are based on. To the
best of our knowledge, data of this size and coverage is the first to be
available in  author disambiguation research. By releasing the data publicly,
we hope to set a benchmark on which further research on author disambiguation
and related topics can  build upon.

\section*{Acknowledgements}

\glnote{todo}

>>>>

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{figures/pub-to-signature}
\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\label{fig:signature}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{figures/workflow}
\caption{Something workflowy...}
\label{fig:workflow}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{figures/cuts}
\caption{Something cutty}
\label{fig:cuts}
\end{figure*}

@@

As part of this study, we also publicly release the annotated data extracted
from the INSPIRE platform, on which our experiments are based on. To the
best of our knowledge, data of this size and coverage is the first to be
available in  author disambiguation research. By releasing the data publicly,
we hope to set a benchmark on which further research on author disambiguation
and related topics can  build upon.

% \section*{Acknowledgements}

% \glnote{todo}
